---
title: "HW 5"
author: "JAYNA CLARK"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#2. 

(a) Use map_data(”state”) from mapdata library to load the data frame which has geographic information for the US
states. Then, filter out the coordinates for California to a new data frame called california.

```{r}
library(ggplot2)
library(tidyr)
library(mapdata)
library(dplyr)
```

```{r}
states <- map_data("state")
california <- states |>
  filter(region == "california")
```

(b) Load wind_turbines.rda from DATA folder to your R environment and select the wind turbines located in California. You can name the new data frame with wind_ca.

```{r}
load("wind_turbines.rda")
wind_ca <- 
  wind_turbines|>
  filter(t_state == "CA")
```

(c) Use ggplot() and geom_polygon() functions to visualize state of California.

```{r}
ggplot() +
  geom_polygon(data = california, aes(x = long, y = lat, group = group),
               fill = "lightgray", color = "black")
```

(d) Once you obtain the map, add your geom_point() function to plot wind turbine locations in CA. If your plot produces a colorbar (legend) please consider adding guides(fill=”none”) to your functions.

```{r}
ggplot() +
  geom_polygon(data = california, aes(x = long, y = lat, group = group), fill = "lightblue3", color = "black",) +
  geom_point(data = wind_ca, aes(x = xlong, y = ylat), color = "orangered", size = 1) +
  guides(fill = "none") +
  coord_fixed(1.3) +
  labs(title = "Wind Turbine Locations in California")

```

